---
title: New in episensr 0.9.3 - Array approach for unmeasured confounders
author: Denis Haine
date: '2018-12-21'
slug: episensr-schneeweiss
categories: ['R', 'epidemiology']
tags: ["epidemiology", "rstats"]
---

New version of
[episensr](https://cran.r-project.org/web/packages/episensr/index.html "R CRAN")
available on CRAN!
Besides now being easier to run [multiple bias
analysis](../episensr-multi), this new version offers the option to
check the effect of residual confounding based on the array and rule-out
approaches ([Schneeweiss,
2006](https://onlinelibrary.wiley.com/doi/abs/10.1002/pds.1200)).

Even after controlling for confounding (in the design or analysis of a study),
some residual confounding  can still be present, because:

1. some confounding factors were not taken into account (not looked at, not
    adjusted for, or no data collected about them),
2. you only losely took into account that confounding (still presence of
    differences between groups after control by matching for example, or you
    lost precision on a confounding variable e.g. by categorizing a continuous
    variable),
3. subjects were not correctly classified to confounding variables.

## Simple sensitivity analyses in the absence of external information: Array approach

The *array approach* by Schneeweis provides a corrected RR based on the
apparent, confounded, RR, the prevalence of the confounding factor among the
exposed and unexposed, and the association between the confounder and the outcome.

Schneeweiss provides the (made-up) example of the association between
TNF\(_\alpha\) blocking agents and Non-Hodgkin (NH) Lymphoma in rheumatoid
arthritis (RA) patients.
Assuming an observed relative risk of 2, that 50% of RA patients have a more
progressive immunologic disease, and that more progressive disease is more
likely to lead to NH lymphoma:

```{r}
library(episensr)
confounders.array(crude.risk = 2,
                  type = "binary",
                  bias_parms = c(2.5, 0.1, 0.5))
```

The function takes values of the observed risk (2.0); if the covariates are
binary, continuous, or on a risk difference scale; the association between
confounder and outcome (let's say here 2.5); the prevalence of the confounder
among the exposed (let's say 0.1); and the prevalence of the confounder among
the unexposed.
The adjusted RR is 3.04.

However, it is more interesting if we could keep some factors constant in our
analysis (the crude risk of 2.0, the prevalence among the unexposed, 0.5), and
vary the imbalance of the hypothetical unoberved confounder (association
confounder-outcome from 1 to 5.5; prevalence among exposed, from 0 to 1):

```{r}
dat <- expand.grid(RR_CD = seq(1, 5.5, 0.5), P_C1 = seq(0, 1, 0.1))
dat$RR_adj <- apply(dat, 1,
                    function(x) confounders.array(2,
                                                  type = "binary",
                                                  bias_parms = c(x[1],
                                                                 x[2],
                                                                 0.5),
                                                  print = FALSE)[5])

```

Then adding fun with 3-d plots!

```{r}
library(lattice)
library(grid)
wireframe(RR_adj ~ RR_CD * P_C1,
          data = dat,
          xlab = "RR\nconfounder-outcome",
          ylab = "Prevalence confounder\namong exposed",
          zlab = "Adjusted\nRR",
          drape = TRUE, colorkey = TRUE,
          scales = list(arrows = FALSE, cex = .5, tick.number = 10,
                        z = list(arrows = FALSE), distance = c(1.5, 1.5, 1.5)),
          zlim = 0:4,
          light.source = c(10, 0, 10),
          col.regions = rainbow(100, s = 1, v = 1,
                                start = 0, end = max(1, 100 - 1) / 100,
                                alpha = .8),
          screen = list(z = -60, x = -60),
          panel = function(...)
          {
              panel.wireframe(...)
              grid.text("Observed RR = 1\nPrevalence confounder\namong unexposed = 0.5",
                        0.125, 0.175, default.units = "native")
          })
```

Good old `lattice`...
But you can have even more fun with `plotly`:

```{r, warning=FALSE, message=FALSE}
RR_CD <- seq(1, 5.5, 0.5)
P_C1 <- seq(0, 1, 0.1)
mat <- outer(RR_CD, P_C1,
             Vectorize(function (i, j)
                 confounders.array(2,
                                   type = "binary",
                                   bias_parms = c(i, j, 0.5),
                                   print = FALSE)[5]))
library(plotly)
plot_ly(x = ~P_C1, y = ~RR_CD, z = ~mat) %>%
    add_surface() %>%
    layout(scene = list(xaxis = list(title = "Pr conf. in exposed", nticks = 5),
                        yaxis = list(title = "RR conf.-RA", nticks = 5),
                        zaxis = list(title = "Adjusted RR", nticks = 5),
                        aspectmode = "cube"))
```

## Using additional information: external adjustment

You can also use additional information not available in the main study to
adjust for the effect of confounding.
Sometimes you can get information from a representative sample to quantify the
imbalance risk factors that are measured among the exposed group; and from the
literature (RCT, observational studies) for the association between the
confounder and the outcome.

We can use the example of Schneeweiss regarding the association between
selective COX-2 inhibitor use and the incidence of MI.

Say we assume an exposure-disease association of 1 (null hypothesis).
The more the truth is away from the null, the more bias in our estimate.
However the less relevant unmeasured confounders become.

Let's try:

```{r}
confounders.ext(RR = 1, bias_parms = c(0.1, 1.6, 0.1, 0.51))
```

Same here, the interest lies in using the function over a range of values, while
keeping some other constant.
And we can extend to several confounders:

```{r}
dat <- expand.grid(RR_CD = seq(0.1, 1, 0.1))
dat$nsaid <- apply(dat, 1,
                   function(x) confounders.ext(1, 
                                               bias_parms = c(x[1], 0.9, 0.1, 0.4),
                                               print = FALSE)[7])
dat$non_user <- apply(dat, 1,
                      function(x) confounders.ext(1, 
                                                  bias_parms = c(x[1], 1.03, 0.09,
                                                                 0.12),
                                                  print = FALSE)[7])
dat$naproxen <- apply(dat, 1,
                      function(x) confounders.ext(1, 
                                                  bias_parms = c(x[1], 1.15, 0.09,
                                                                 0.79),
                                               print = FALSE)[7])
dat$rof_napro <- apply(dat, 1,
                       function(x) confounders.ext(1, 
                                               bias_parms = c(x[1], 1.6, 0.1, 0.51),
                                               print = FALSE)[7])
library(tidyverse)
dat2 <- dat %>% gather(nsaid, non_user, naproxen, rof_napro,
                       key = "COX2", value = "bias_perc")
library(ggplot2)
ggplot(dat2, aes(x = RR_CD, y = bias_perc, group = COX2, colour = COX2)) +
    geom_line() +
    scale_colour_brewer(palette = "Dark2",
                        labels = c("COX-2 vs. naproxen", "COX-2 vs. non-users",
                                   "COX-2 vs. non-selective NSAIDs",
                                   "Rofecoxib vs. naproxen")) +
    geom_vline(xintercept = 0.7) +
    xlab("Association Confounder-Disease (RR)") +
    ylab("Bias of Exposure-Disease Association (RR) in %") +
    ggtitle(expression(paste("Bias as a function of misspecification of the ", RR[CD], " from the literature"))) +
    theme(legend.position = c(.8, .3),
          legend.title = element_blank()) +
    annotate("text", label = expression(paste("Literature estimate ", RR[CD], " = 0.7")), x = 0.6, y = -3.75)
```
