---
title: New in episensr 0.9.3 - Multiple bias analysis
author: Denis Haine
date: '2018-12-21'
slug: episensr-multi
categories: ['R', 'epidemiology']
tags: ["epidemiology", "rstats"]
---

New version of
[episensr](https://cran.r-project.org/web/packages/episensr/index.html "R CRAN")
available on CRAN!
Now you can more easily run multiple bias analysis.
Very often, epidemiologic studies suffer from multiple biases.
Up to now, it took a bit of "manipulation" to apply a sequence of bias function
from `episensr`.
So here's the function `multiple.bias` that allows to pipe corrected 2-by-2
table from one bias function to an other.

Let's take for example the study from [Chien et al,
2006](https://www.ncbi.nlm.nih.gov/pubmed/16322894) looking at the association
between antidepressant use (AD) and breast cancer (BC):

```{r}
chien <- matrix(c(118, 832, 103, 884),
                dimnames = list(c("BC+", "BC-"), c("AD+", "AD-")),
                nrow = 2, byrow = TRUE)
library(knitr)
kable(chien)
```

Antidepressant use was established based on pharmacy records.
However this information was not available for every participant, self-report of
medication was also used leading to a possible misclassification.
The cross-classification frequencies of interview responses and pharmacy records
allowed to determine sensitivity (Se) and specificity (Sp) for cases and
controls, used in the misclassification bias sensitivity analysis:

```{r}
library(episensr)
library(magrittr)
chien %>% misclassification(., type = "exposure", bias_parms = c(.56, .58, .99, .97))
```

Let's follow this bias by a selection bias:

```{r}
chien %>% 
    misclassification(., type = "exposure", bias_parms = c(.56, .58, .99, .97)) %>%
    multiple.bias(., bias_function = "selection", bias_parms = c(.73, .61, .82, .76))
```

The `misclassification` output is piped (`%>%`) into the `selection` bias
function thanks to `multiple.bias`.
We can also add an unmeasured confounder the same way:

```{r}
chien %>%
    misclassification(., type = "exposure", bias_parms = c(.56, .58, .99, .97)) %>%
    multiple.bias(., bias_function = "selection",
                  bias_parms = c(.73, .61, .82, .76)) %>%
    multiple.bias(., bias_function = "confounders",
                  type = "OR", bias_parms = c(.92, .3, .44))
```

### Probabilistic methods

The same can be realized within a probabilistic framework with the `probsens`
series of functions.
Let's look first at each single bias analysis, then by combining them.

#### Misclassification

```{r}
set.seed(123)
mod1 <- chien %>%
    probsens(., type = "exposure", reps = 100000,
             seca.parms = list("trapezoidal", c(.45, .5, .6, .65)),
             seexp.parms = list("trapezoidal", c(.4, .48, .58, .63)),
             spca.parms = list("trapezoidal", c(.95, .97, .99, 1)),
             spexp.parms = list("trapezoidal", c(.96, .98, .99, 1)),
             corr.se = .8, corr.sp = .8)
```

```{r, fig.cap='Misclassification bias.'}
library(ggplot2)
ggplot(mod1$sim.df, aes(x = corr.OR)) + 
    geom_histogram(aes(y = ..density..), colour = "black", fill = "white") +
    geom_density(alpha = .2, fill = "#FF6666") +
    labs(title = "1. Misclassification bias",
         x = "OR without random error incorporated") +
    coord_cartesian(xlim = c(0, 3))
```

#### Selection bias

```{r}
set.seed(123)
mod2 <- chien %>%
    probsens.sel(., reps = 100000,
                 case.exp = list("logit-normal", c(-1.1, 0, 0, 1)),
                 case.nexp = list("trapezoidal", c(.75, .85, .95, 1)),
                 ncase.exp = list("logit-normal", c(-1.2, 0, 0, 1)),
                 ncase.nexp = list("trapezoidal", c(0.7, 0.8, 0.9, 1)))
```

```{r, fig.cap='Selection bias'}
ggplot(mod2$sim.df, aes(x = corr.or)) + 
    geom_histogram(aes(y = ..density..), colour = "black", fill = "white") +
    geom_density(alpha = .2, fill = "#FF6666") +
    labs(title = "2. Selection bias",
         x = "OR without random error incorporated") +
    coord_cartesian(xlim = c(0, 3))
```
#### Confounding

```{r}
set.seed(123)
mod3 <- chien %>%
    probsens.conf(., reps = 100000,
                  prev.exp = list("logit-normal", c(-0.75, 0.8, 0, 1)),
                  prev.nexp = list("logit-normal", c(-0.4, 0.8, 0, 1)),
                  risk = list("trapezoidal", c(.2, .58, 1.01, 1.24)))
```

```{r, fig.cap='Confounding.'}
ggplot(mod3$sim.df, aes(x = OR.SMR.or)) + 
    geom_histogram(aes(y = ..density..), colour = "black", fill = "white") +
    geom_density(alpha = .2, fill = "#FF6666") +
    labs(title = "3. Confounding bias",
         x = "OR without random error incorporated") +
    coord_cartesian(xlim = c(0, 3))
```

#### Model 2 then model 3

```{r}
set.seed(123)
chien %>%
    probsens(., type = "exposure", reps = 100000,
             seca.parms = list("trapezoidal", c(.45, .5, .6, .65)),
             seexp.parms = list("trapezoidal", c(.4, .48, .58, .63)),
             spca.parms = list("trapezoidal", c(.95, .97, .99, 1)),
             spexp.parms = list("trapezoidal", c(.96, .98, .99, 1)),
             corr.se = .8, corr.sp = .8) %>%
    multiple.bias(., bias_function = "probsens.sel",
                  case.exp = list("logit-normal", c(-1.1, 0, 0, 1)),
                  case.nexp = list("trapezoidal", c(.75, .85, .95, 1)),
                  ncase.exp = list("logit-normal", c(-1.2, 0, 0, 1)),
                  ncase.nexp = list("trapezoidal", c(0.7, 0.8, 0.9, 1)))
```

#### Model 2 then model 3 then model 4

```{r}
set.seed(123)
mod6 <- chien %>%
    probsens(., type = "exposure", reps = 100000,
             seca.parms = list("trapezoidal", c(.45, .5, .6, .65)),
             seexp.parms = list("trapezoidal", c(.4, .48, .58, .63)),
             spca.parms = list("trapezoidal", c(.95, .97, .99, 1)),
             spexp.parms = list("trapezoidal", c(.96, .98, .99, 1)),
             corr.se = .8, corr.sp = .8) %>%
    multiple.bias(., bias_function = "probsens.sel",
                  case.exp = list("logit-normal", c(-1.1, 0, 0, 1)),
                  case.nexp = list("trapezoidal", c(.75, .85, .95, 1)),
                  ncase.exp = list("logit-normal", c(-1.2, 0, 0, 1)),
                  ncase.nexp = list("trapezoidal", c(0.7, 0.8, 0.9, 1))) %>% 
    multiple.bias(., bias_function = "probsens.conf",
                  prev.exp = list("logit-normal", c(-0.75, 0.8, 0, 1)),
                  prev.nexp = list("logit-normal", c(-0.4, 0.8, 0, 1)),
                  risk = list("trapezoidal", c(.2, .58, 1.01, 1.24)))
```

```{r, fig.cap='Misclassification followed by selection bias and then confounding bias.'}
ggplot(mod6$sim.df, aes(x = OR.SMR.or)) + 
    geom_histogram(aes(y = ..density..), colour = "black", fill = "white") +
    geom_density(alpha = .2, fill = "#FF6666") +
    labs(title = "6. Misclassification, then\nselection, then confounding bias",
         x = "OR without random error incorporated") +
    coord_cartesian(xlim = c(0, 3))
```

```{r, fig.cap='Same as previous figure but with random error incorporated.'}
ggplot(mod6$sim.df, aes(x = tot.ORadj.smr)) + 
    geom_histogram(aes(y = ..density..), colour = "black", fill = "white") +
    geom_density(alpha = .2, fill = "#FF6666") +
    labs(title = "6. Misclassification, then\nselection, then confounding bias",
         x = "OR with random error incorporated") +
    coord_cartesian(xlim = c(0, 3))
```
