---
title: Episensr 0.9.0 now available on CRAN
author: Denis Haine
date: '2017-08-21'
slug: episensr-090-rmd
categories: ['R']
tags: ["episensr", "#rstats"]
---

A small update for my [`episensr`](https://cran.r-project.org/package=episensr
"episensr") R package is now available on CRAN.
The update focus on misclassification.

First, covariate misclassification is now available, via the function
`misclassification_cov`.
For example, the paper by [Berry et
al.](http://www.bmj.com/content/330/7495/815) looked if misclassification of the
confounding variable _in vitro fertilization_ (IVF), a confounder, resulted
wrongly on an association between increase folic acid and having twins.
IVF increases the risk of twins, and women undergoing IVF might be more likely
to take folic acid supplements, i.e. IVF would be a confounder between vitamins
and twins.
Data on IVF were not available and a proxy for it was used, _period of
involuntary childlessness_.
However, it was a poor proxy for IVF, with a sensitivity of 60% and a
specificity of 95%.
These bias parameters were assumed to be nondifferential.
Here's the code with `episensr`:

```{r}
library(episensr)

misclassification_cov(array(c(1319, 38054, 5641, 405546, 565, 3583,
                              781, 21958, 754, 34471, 4860, 383588),
                            dimnames = list(c("Twins+", "Twins-"),
                                            c("Folic acid+", "Folic acid-"),
                                            c("Total", "IVF+", "IVF-")),
                            dim = c(2, 2, 3)),
                      bias_parms = c(.6, .6, .95, .95))
```

While the non-adjusted analysis showed that women taking folic acid were 2.44
times more likely to have twins, after correcting for the misclassification of
IVF, risk ratio is now null (= 1.0).

Second, confidence intervals for corrected association due to exposure
misclassification are now available.
While previously you could already bootstrapped the estimates, you can also now
get the confidence intervals from the variance of the corrected odds ratio
estimator, as in [Greenland et
al.](http://onlinelibrary.wiley.com/doi/10.1002/sim.4780070704/full#abstract)
and [Chu et
al.](http://www.sciencedirect.com/science/article/pii/S1047279706000688).
Using the example in Chu et al. of a case-control study of cigarette smoking and
invasive pneumococcal disease, the unadjusted odds ratio is 4.32, with a 95%
confidence interval of 2.96 to 6.31.
Let's say the sensitivity of self-reported smoking is 94% and specificity is
97%, for both the case and control groups:

```{r}
misclassification(matrix(c(126, 92, 71, 224),
                         dimnames = list(c("Case", "Control"),
                                         c("Smoking +", "Smoking - ")),
                         nrow = 2, byrow = TRUE),
                  type = "exposure",
                  bias_parms = c(0.94, 0.94, 0.97, 0.97))
```

The corrected odds ratio is now 5.02, with a widened 95% confidence interval
(3.28 to 7.69).
Note the bias despite the large sensitivity and specificity.

You can even reproduce the contour plots in Chu et al. paper!

```{r, fig.cap='Contour plot of point estimate of corrected odds ratio (OR)'}
dat <- expand.grid(Se = seq(0.582, 1, 0.02),
                   Sp = seq(0.762, 1, 0.02))

dat$OR_c <- apply(dat, 1,
                  function(x) misclassification(matrix(c(126, 92, 71, 224),
                                                       nrow = 2, byrow = TRUE),
                                                type = "exposure",
                                                bias_parms = c(x[1], x[1], x[2], x[2]))$adj.measures[2, 1])
dat$OR_c <- round(dat$OR_c, 2)

library(ggplot2)
library(directlabels)
p1 <- ggplot(dat, aes(x = Se, y = Sp, z = OR_c)) +
    geom_contour(aes(colour = ..level..), breaks = c(4.32, 6.96, 8.56, 12.79, 23.41, 432.1)) +
    annotate("text", x = 1, y = 1, label = "4.32", size = 4) +
    scale_fill_gradient(limits = range(dat$OR_c), high = 'red', low = 'green') +
    scale_x_continuous(breaks = seq(0.5, 1, .1), expand = c(0,0)) +
    scale_y_continuous(breaks = seq(0.5, 1, .1), expand = c(0,0)) +
    coord_fixed(ylim = c(0.5, 1.025), xlim = c(0.5, 1.025)) +
    scale_colour_gradient(guide = 'none') +
    theme(plot.title = element_text(face = "bold", size = 16),
          axis.title = element_text(face="bold", size = 14),
          axis.text.y = element_text(colour="grey42", size = 12),
          axis.text.x = element_text(colour="grey42", size = 12),
          legend.position = "none") +
    xlab("Sensitivity") +
    ylab("Specificity") +
    ggtitle("Estimate of Corrected OR")
direct.label(p1, list("far.from.others.borders", "calc.boxes", "enlarge.box", 
                           hjust=1, vjust=-.5, box.color = NA, cex = .9,
                           fill = "transparent", "draw.rects"))
```

```{r, fig.cap='Contour plot of 95% lower confidence limit of corrected OR'}
dat$ORc_lci <- apply(dat, 1,
                     function(x) misclassification(matrix(c(126, 92, 71, 224),
                                                          nrow = 2, byrow = TRUE),
                                                   type = "exposure",
                                                   bias_parms = c(x[1], x[1], x[2], x[2]))$adj.measures[2, 2])
dat$ORc_lci <- round(dat$ORc_lci, 2)

p3 <- ggplot(dat, aes(x = Se, y = Sp, z = ORc_lci)) +
    geom_contour(aes(colour = ..level..),
                 breaks = c(4.05, 4.64, 5.68, 7.00, 9.60)) +
    annotate("text", x = 1, y = 1, label = "2.96", size = 4) +
    scale_fill_gradient(limits = range(dat$ORc_lci), high = 'red', low = 'green') +
    scale_x_continuous(breaks = seq(0.5, 1, .1), expand = c(0,0)) +
    scale_y_continuous(breaks = seq(0.5, 1, .1), expand = c(0,0)) +
    coord_fixed(ylim = c(0.5, 1.025), xlim = c(0.5, 1.025)) +
    scale_colour_gradient(guide = 'none') +
    theme(plot.title = element_text(face = "bold", size = 16),
          axis.title = element_text(face="bold", size = 14),
          axis.text.y = element_text(colour="grey42", size = 12),
          axis.text.x = element_text(colour="grey42", size = 12),
          legend.position = "none") +
    xlab("Sensitivity") +
    ylab("Specificity") +
    ggtitle("95% LCI of Corrected OR")
direct.label(p3, list("far.from.others.borders", "calc.boxes", "enlarge.box", 
                           hjust=1, vjust=-.5, box.color = NA, cex = .9,
                           fill = "transparent", "draw.rects"))
```
