---
title: Scientific collaboration patterns in cattle health research in Canada
author: Denis Haine
date: '2017-10-11'
slug: dairyres-rmd
categories: ['R', 'epidemiology']
tags: ["dairy", "cow", "rstats", "epidemiology"]
---

I was curious to see if I could identify some patterns of collaboration and
research topics in cow health research made in Canada.
For this, I'm trying the R package
[`bibliometrix`](https://cran.r-project.org/package=bibliometrix "bibliometrix").
This package allows quantitative research in scientometrics and bibliometrics by
providing different routines for importing bibliographic data from
[Scopus](https://www.scopus.com/ "Scopus") and [ISI Web of
Knowledge](http://www.webofknowledge.com/ "Web of Knowledge") databases, and
performing various bibliometric analyses.
The [Bibliometrix website](http:\\www.bibliometrix.com) provides a good tutorial
that I will mainly follow, with the sole objective to satisfy my curiosity and
have fun!

As explained in the `bibliometrix` tutorial, bibliographic data were retrieved
from ISI Web of Knowledge, Web of Science Core Collection database.
The following descriptors of thematics were used:

> TS=(ruminant OR cow OR bovine OR cattle OR calf)  AND PY=(2012-2017) AND TS=(coccidiosis
OR Pasteurella OR mastitis OR parvovirus OR PPV OR mummification OR
stillbirth OR "foot-and-mouth disease" OR FMD "Aphtous fever" OR pneumonia OR
streptococci OR "E. coli" OR tuberculosis OR brucellosis OR salmonellosis OR
salmonella OR anthrax OR babesiosis OR piroplasmosis OR "tick fever" OR "red
water" OR babesia OR sarcocystosis OR sarcosystis OR toxoplasmosis OR toxoplasma
OR streptococcus OR clostridium OR influenza OR leptospirosis OR mycoplasma OR
rotavirus OR BSE OR prion OR TSE OR "mad cow" OR metritis OR encephalitis OR
biotin OR "energy balance" OR "drug resistance" OR mannheimia OR
escherichia-coli OR "bovine respiratory disease" OR "subclinical ketosis" OR
beta-hydroxybutyrate OR campylobacter OR epidemic OR "viral hemorrhagic fever"
OR O157H7 OR lameness OR diarrhea OR "necrotic enteritis" OR "zoonotic pathogen"
OR zoonosis OR q-fever OR "animal welfare" OR giardia OR paratuberculosis OR
coxiella OR coxiellosis OR "Johne's disease" OR "uterine disease" OR
endometritis OR reproductive-performance OR "west nile virus" OR PrPSc OR
cesarean-section OR aureus OR staphylococcus OR epidermidis OR eimeria OR
coccidia OR haemonchus OR "metabolic disease" OR ketosis OR "O157:H7" OR
foot-and-mouth OR pseudomonas OR "airborne transmission" OR "foodborne
transmission" OR "gastrointestinal nematodes" OR ixodes OR "tick-borne disease"
OR borreliosis OR "failure of transfer of passive immunity" OR mycotoxins OR
"antimicrobial resistance" OR enterococcus OR "foodborne pathogens" OR "somatic
cell count" OR agalactiae OR mastitis OR "staphylococcus aureus" OR "MRSA" OR
uberis OR "subacute ruminal acidosis" OR "pregnancy loss" OR fertility OR
anovulation OR "udder health" OR "bovine spongiform encephalopathy" OR scrapie
OR "bulk milk somatic cell count" OR "downer cow syndrome" OR "milk fever" OR
mycobacterium OR listeria OR rotavirus OR "intramammary infection" OR parasitism
OR borrelia OR bluetongue OR BVD OR "bovine viral diarrhea" OR abortion OR
vibriosis OR "cystic ovaries" OR neosporosis OR "repeat breeding syndrome" OR
"retained fetal membranes" OR schmallenberg OR acetonaemia OR "fatty liver" OR
acidosis OR "calf scour" OR IBR OR "digital dermatitis" OR "foot rot" OR
"epizootic hemorrhagic disease" OR lice OR mange OR ringworm OR "sole ulcer" OR
"displaced abomasum" OR botulism OR rabies) AND LA=(English OR French) AND
DT=(Article OR Review) AND CU=(Canada)

i.e. articles or reviews published between 2012 and now (October 2017), in
English or French, under the SCI-EXPANDED citation index, for Canada.
The ISI website only allows to export 500 records at a time.
So several files were exported in bibtex format, then merged together and their
leading white spaces removed thanks to a small bash script:

```{shell, eval=FALSE}
cat *.bib >> records.bib
sed "s/^[ \t]*//" -i records.bib
```

Then we can load the R package and read the data!

```{r}
library(bibliometrix)
```

```{r, include=FALSE}
D <- readFiles("~/workspace/h/haine/SciCoPatt/data/records.bib")
M <- convert2df(D, dbsource = "isi", format = "bibtex")
library(tidyverse)
library(ggthemes)
library(stringr)

results <- biblioAnalysis(M, sep = ";")

address <- as.data.frame(table(results$FirstAffiliation))
address$reprint_author <- gsub("\\(.*$", "", address[, 1])
address$org <- sapply(strsplit(as.character(address[, 1]), ','), "[", 3)
address$org <- trimws(address$org, which = "left")

address$country <- str_extract(address[, 1], '\\b[^,]+$')
address$country2 <- str_extract(address[, 1], '\\b[^( )]+$')
address$country <- gsub("[.]", "", address$country)
address$country2 <- gsub("[.]", "", address$country2)
address$country <- with(address, ifelse(country2 == "USA", "USA", country))
address$country <- with(address, ifelse(country == "ENGLAND" |
                                        country == "NORTH IRELAND" |
                                        country == "SCOTLAND" |
                                        country == "WALES", "UNITED KINGDOM", country))
address$country <- with(address, ifelse(country == "REUNION" |
                                        country == "GUADELOUPE", "FRANCE", country))

address$org <- with(address, ifelse(org == "ELLINBANK", "ELLINBANK CTR", org))
address$org <- with(address, ifelse(org == "INST TROP MED" & country == "BELGIUM",
                                    "INST TROP MED ANTWERP", org))
address$org <- with(address, ifelse(org == "NATL DAIRY RES INST",
                                    "NATL DAIRY RES INST HARYANA", org))
address$org <- with(address, ifelse(org == "UNIV MED CTR",
                                    "UNIV MED CTR GOTTINGEN", org))
address$org <- with(address, ifelse(org == "NATL RES CTR",
                                    "NATL RES CTR CAIRO", org))
address$org <- with(address, ifelse(org == "EST EL ENCUENTRO RES \\& EXTENS FARM RUMINANT NUTR",
                                    "EST EL ENCUENTRO RES \\& EXTENS FARM RUMINANT NUTR BUENOS AIRES", org))
address$org <- with(address, ifelse(org == "CTR RIC PROD FORAGGERE \\& LATTIERO CASEARIE SEDE D",
                                    "CTR RIC PROD FORAGGERE \\& LATTIERO CASEARIE", org))
address$org <- with(address, ifelse(org == "VIA PORCELLASCO 7",
                                    "CTR RIC PROD FORAGGERE \\& LATTIERO CASEARIE", org))
address$org <- with(address, ifelse(org == "VET DISPENSARY",
                                    "VET DISPENSARY KERALA", org))
address$org <- with(address, ifelse(org == "UNIV FED MINAS GERAIS MICROBIOL",
                                    "UNIV FED MINAS GERAIS", org))
address$org <- with(address, ifelse(org == "SWEDISH UNIV AGR SCI SLU UPPSALA",
                                    "SWEDISH UNIV AGR SCI", org))
address$org <- with(address, ifelse(org == "SWEDISH UNIV AGR SCI SLU",
                                    "SWEDISH UNIV AGR SCI", org))
address$org <- with(address, ifelse(org == "NATL VET LAB" & country == "PAKISTAN",
                                    "NATL VET LAB PAKISTAN", org))
address$org <- with(address, ifelse(org == "NATL VET LAB" & country == "LITHUANIA",
                                    "NATL VET LAB LITHUANIA", org))
address$org <- with(address, ifelse(org == "POB 80216",
                                    "KING ABDULAZIZ UNIV", org))

address$org <- with(address, ifelse(org == "DOCKLITZER TOR 11",
                                    "", org))
address$org <- with(address, ifelse(org == "UNIV AGR KRAKOW",
                                    "AGR UNIV KRAKOW", org))
address$org <- with(address, ifelse(org == "18830 RD 112",
                                    "UNIV CALIF DAVIS", org))
address$org <- with(address, ifelse(org == "UL GLEBOKA 30",
                                    "", org))
address$org <- with(address, ifelse(org == "ARS",
                                    "USDA ARS", org))

address$org <- with(address, ifelse(org == "ECOLE NATL VET" & (reprint_author == "ADJOU, KT" | reprint_author == "CARSTANJEN, B" | reprint_author == "GRIMARD, B" | reprint_author == "GUILLOT, J"),
                                    "ENV MAISONS ALFORT", org))
address$org <- with(address, ifelse(org == "UMR MYCOPLASMOSES RUMINANTS ANSES VETAGRO SUP VET" | org == "ENV ALFORT" | org == "ENV DALFORT" | org == "ENVA",
                                    "ENV MAISONS ALFORT", org))
address$org <- with(address, ifelse(org == "ECOLE NATL VET" & (reprint_author == "BAREILLE, N" | reprint_author == "BEAUDEAU, F" | reprint_author == "LE BIZEC, B"),
                                    "ECOLE NATL VET NANTES", org))
address$org <- with(address, ifelse(org == "ECOLE NATL VET" & (reprint_author == "CAVRET, S" | reprint_author == "FREMAUX, B"),
                                    "ECOLE NATL VET MARCY LETOILE", org))

address$org <- with(address, ifelse(org == "BIOFORSK",
                                    "BIOFORSK NORWEGIAN INST AGR \\& ENVIRONM RES", org))
address$org <- with(address, ifelse(org == "RUA SANTA LUZIA 206",
                                    "", org))
address$org <- with(address, ifelse(org == "KATHOLIEKE UNIV LEUVEN BIOSYST MEBIOS KU LEUVEN",
                                    "KATHOLIEKE UNIV LEUVEN", org))
address$org <- with(address, ifelse(org == "COLL VET MED" & country == "USA",
                                    "KANSAS STATE UNIV", org))
address$org <- with(address, ifelse(org == "COLL VET MED" & country == "IRAQ",
                                    "BAGHDAD UNIV", org))
address$org <- with(address, ifelse(org == "COLL VET MED" & country == "INDIA",
                                    "PUNJAB UNIV", org))
address$org <- with(address, ifelse(org == "COLL VET MED" & country == "IRAN",
                                    "TEHRAN UNIV", org))
address$org <- with(address, ifelse(org == "NATL VET INST" & country == "SWEDEN",
                                    "NATL VET INST SWEDEN", org))
address$org <- with(address, ifelse(org == "NATL VET INST" & country == "NORWAY",
                                    "NATL VET INST NORWAY", org))
address$org <- with(address, ifelse(org == "NATL VET INST" & country == "ETHIOPIA",
                                    "NATL VET INST ETHIOPIA", org))

address$org <- with(address, ifelse(org == "BP 12",
                                    "", org))
address$org <- with(address, ifelse(org == "1945 INOKASHIRA",
                                    "SHIZUOKA PREF RES INST ANIM IND", org))
address$org <- with(address, ifelse(org == "POB 14155-6453",
                                    "UNIV TEHRAN", org))
address$org <- with(address, ifelse(org == "VET COLL \\& RES INST",
                                    "VET COLL \\& RES INST INDIA", org))

address$org <- with(address, ifelse(org == "POB 80283",
                                    "", org))

address$org <- with(address, ifelse(org == "CARRETERA TOLUCA TEJUPILCO KM 67-5",
                                    "", org))
address$org <- with(address, ifelse(org == "CALZ DEL HUESO 1100 COL",
                                    "", org))
address$org <- with(address, ifelse(org == "SLU",
                                    "SWEDISH UNIV AGR SCI", org))
address$org <- with(address, ifelse(org == "FAC VET" & (reprint_author == "ABUELO, A" | reprint_author == "DIEGUEZ, FJ"),
                                    "UNIV SANTIAGO", org))
address$org <- with(address, ifelse(org == "FAC VET" & country == "SLOVENIA",
                                    "UNIV LJUBLJANA", org))
address$org <- with(address, ifelse(org == "FAC VET" & country == "URUGUAY",
                                    "UNIV MONTEVIDEO", org))
address$org <- with(address, ifelse(org == "FAC VET" & country == "ITALY",
                                    "UNIV TORINO", org))
address$org <- with(address, ifelse(org == "VET RES INST",
                                    "VET RES INST BRNO", org))

address$org <- with(address, ifelse(org == "COLL AGR \\& VET MED",
                                    "COLL AGR \\& VET MED QASSIM", org))

address$org <- with(address, ifelse(org == "2265G ANTHONY HALL",
                                    "MICHIGAN STATE UNIV", org))

address$org <- with(address, ifelse(org == "VETERINARPL 1",
                                    "UNIV VET MED VIENNA", org))

address$org <- with(address, ifelse(org == "ALBERTA AGR FOOD",
                                    "ALBERTA AGR \\& FOOD", org))
address$org <- with(address, ifelse(org == "SUITE 204",
                                    "ALBERTA AGR \\& RURAL DEV", org))

address$org <- with(address, ifelse(org == "224 TRIKALON STR",
                                    "UNIV THESSALY", org))
address$org <- with(address, ifelse(org == "POB 8146 DEP",
                                    "NATL VET INST NORWAY", org))

address$org <- with(address, ifelse(org == "COLL VET SCI",
                                    "COLL VET SCI ANDHRA PRADESH", org))
address$org <- with(address, ifelse(org == "FAC AGR" & country == "CROATIA",
                                    "FAC AGR OSIJEK", org))
address$org <- with(address, ifelse(org == "FAC AGR" & country == "ITALY" & (reprint_author == "CALAMARI, IL"),
                                    "FAC AGR PIACENZA", org))
address$org <- with(address, ifelse(org == "FAC AGR" & country == "ITALY" & (reprint_author == "SEVI, A"),
                                    "FAC AGR FOGGIA", org))
address$org <- with(address, ifelse(org == "FAC AGR" & country == "SERBIA" & (reprint_author == "GLAMOCLIJA, D" | reprint_author == "MALETIC, R"),
                                    "FAC AGR BELGRADE", org))
address$org <- with(address, ifelse(org == "FAC AGR" & country == "SERBIA" & (reprint_author == "KUCEVIC, D" | reprint_author == "STEVANCEVIC, M" | reprint_author == "VIDOVIC, V"),
                                    "FAC AGR NOVI SAD", org))

address$org <- with(address, ifelse(org == "NATL AGR RES CTR" & country == "PAKISTAN",
                                    "NATL AGR RES CTR ISLAMABAD", org))
address$org <- with(address, ifelse(org == "NATL AGR RES CTR" & country == "JAPAN" & reprint_author == "AOKI, M",
                                    "NATL AGR RES CTR HOKKAIDO REG", org))
address$org <- with(address, ifelse(org == "NATL AGR RES CTR" & country == "JAPAN" & reprint_author == "KAMIYA, M",
                                    "NATL AGR RES CTR KUMAMOTO", org))

address$org <- with(address, ifelse(org == "POB 12",
                                    "HEBREW UNIV JERUSALEM", org))
address$org <- with(address, ifelse(org == "PASSAGE DEPORTES 2",
                                    "UNIV LIEGE", org))
address$org <- with(address, ifelse(org == "PRIVATE BAG 3123",
                                    "AGRESEARCH", org))

address$org <- with(address, ifelse(org == "UAEM",
                                    "UNIV AUTONOMA ESTADO MEXICO", org))
address$org <- with(address, ifelse(org == "NEIKER TECN",
                                    "NEIKER TECNALIA", org))
address$org <- with(address, ifelse(org == "LA SALLE UNIV",
                                    "UNIV LA SALLE BOGOTA", org))
address$org <- with(address, ifelse(org == "NATL INST HLTH SCI",
                                    "NATL INST HLTH SCI TOKYO", org))
address$org <- with(address, ifelse(org == "98 8TH ALLEY",
                                    "UNIV TEHRAN", org))

address$org <- with(address, ifelse(org == "1 BEICHEN WEST RD",
                                    "CHINESE ACAD SCI", org))
address$org <- with(address, ifelse(org == "1 PK DR BUNDOORA",
                                    "", org))
address$org <- with(address, ifelse(org == "1 SHIELDS AVE",
                                    "UNIV CALIF DAVIS", org))
address$org <- with(address, ifelse(org == "1 UNIV ARKANSAS",
                                    "UNIV ARKANSAS", org))
address$org <- with(address, ifelse(org == "1-1 ROKKODAI CHO NADA",
                                    "KOBE UNIV", org))
address$org <- with(address, ifelse(org == "1-1-1 YAYOI",
                                    "TOKYO UNIV", org))
address$org <- with(address, ifelse(org == "1001 DONNA CT",
                                    "", org))
address$org <- with(address, ifelse(org == "10A EPIMENIDOU STR",
                                    "", org))
address$org <- with(address, ifelse(org == "111 CECILIO URBINA",
                                    "", org))
address$org <- with(address, ifelse(org == "1110 SHIMOGATOU",
                                    "YAMANASHI UNIV", org))

address$org <- with(address, ifelse(org == "1122 HEXAM ST" | org == "122 A HEXAM ST" | org == "122A HEXAM ST" | org == "125 LOYALIST DR" | org == "13 FERNDALE" | org == "130A JALAN AWAN JAWA" | org == "15-107" | org == "151",
                                    "", org))
address$org <- with(address, ifelse(org == "1207 W GREGORY DR",
                                    "UNIV ILLINOIS", org))
address$org <- with(address, ifelse(org == "1287 ANTHONY HALL",
                                    "MICHIGAN STATE UNIV", org))
address$org <- with(address, ifelse(org == "135 CALL HALL",
                                    "KANSAS STATE UNIV", org))
address$org <- with(address, ifelse(org == "UNIV MINNESOTA TWIN CITIES" | org == "1365 GORTNER AVE" | org == "136F ANDREW BOSS LAB MEAT SCI",
                                    "UNIV MINNESOTA", org))
address$org <- with(address, ifelse(org == "138 BOSZORMENYI U",
                                    "UNIV DEBRECEN", org))
address$org <- with(address, ifelse(org == "1400 NORTH CAMPUS DR",
                                    "S DAKOTA STATE UNIV", org))
address$org <- with(address, ifelse(org == "1523 CENTENNIAL BLVD",
                                    "N DAKOTA STATE UNIV", org))
address$org <- with(address, ifelse(org == "UNIV N DAKOTA",
                                    "N DAKOTA STATE UNIV", org))
address$org <- with(address, ifelse(org == "159 IND N RD",
                                    "SHANDONG ACAD AGR SCI", org))
address$org <- with(address, ifelse(org == "SHANDONG AGR \\& ENG UNIV" | org == "SHANDONG AGR UNIV" | org == "159-1 IND N RD",
                                    "SHANDONG ACAD AGR SCI", org))
address$org <- with(address, ifelse(org == "AGR \\& AGR FOOD CANADA",
                                    "AGR \\& AGRI FOOD CANADA", org))
address$org <- with(address, ifelse(org == "ZOETIS UK LTD",
                                    "ZOETIS INC", org))
address$org <- with(address, ifelse(org == "ZIMBABWE.",
                                    "INT CROPS RES INST", org))
address$org <- with(address, ifelse(org == "ZHEJIANG A\\&F UNIV" | org == "ZHEJIANG ACAD AGR SCI",
                                    "ZHEJIANG UNIV", org))
address$org <- with(address, ifelse(org == "YILDIZ TEKN UNIV",
                                    "YILDIZ TECH UNIV", org))
address$org <- with(address, ifelse(org == "WROCLAW UNI ENVIRONM \\& LIFE SCI" | org == "WROCLAW UNIV LIFE SCI" | org == "WROCLAW UNIV TECHNOL",
                                    "WROCLAW UNIV ENVIRONM \\& LIFE SCI", org))
address$org <- with(address, ifelse(org == "WHO",
                                    "WORLD HLTH ORG", org))
address$org <- with(address, ifelse(org == "WESTPOMERANIAN UNIV TECHNOL SZCZECIN" | org == "WESTPOMMERSCHE TECH UNIV SZCZECIN" | org == "WESTPOMERANIAN UNIV TECHNOL" | org == "WEST POMERANIAN UNIV TECHNOL SZCZECIN",
                                    "WEST POMERANIAN UNIV TECHNOL", org))
address$org <- with(address, ifelse(org == "WESTERN CAPE",
                                    "WESTERN CAPE DEPT AGR", org))
address$org <- with(address, ifelse(org == "WASHINGTON UNIV",
                                    "WASHINGTON STATE UNIV", org))
address$org <- with(address, ifelse(org == "YALELAAN 7" | org == "UNIV MED CTR UTRECHT" | org == "FAC DIERGENEESKUNDE UTRECHT" | org == "VET FAC UTRECHT",
                                    "UNIV UTRECHT", org))
address$org <- with(address, ifelse(org == "UNIWERSTET PRZYRODNICZY WROCLAWIU" | org == "UNIWERSYTET PRZYRODNICZY LUBLINIE" | org == "UNIWERSYTET PRZYRODNICZY WE WROCLAWIU" | org == "UNIWERSYTET PRZYRODNICZY WROCLAWIU" | org == "WOLYNSKA STR 33",
                                    "UNIWERSYTET PRZYRODNICZY", org))
address$org <- with(address, ifelse(org == "WESTERN COLL VET MED",
                                    "UNIV SASKATCHEWAN", org))
address$org <- with(address, ifelse(org == "WARSAW UNIV TECHNOL" | org == "WARSAW UNIV LIFE SCI" | org == "WARSAW UNIV LIFE SCI SGGW" | org == "WARSAW UNIV LIFE SCI WULS SGGW",
                                    "WARSAW UNIV", org))
address$org <- with(address, ifelse(org == "WALTON MANOR" | org == "MSD ANIM HLTH GMBH",
                                    "MSD ANIM HLTH", org))

address$org <- with(address, ifelse(org == "WALLOON AGR RES CTR CRA W",
                                    "WALLOON AGR RES CTR", org))
address$org <- with(address, ifelse(org == "WAGENINGEN INST ANIM SCI" | org == "WAGENINGEN LIVESTOCK RES" | org == "WAGENINGEN UNIV \\& RES" | org == "WAGENINGEN UNIV \\& RES CTR" | org == "WAGENINGEN UNIV \\& RES CTR CVI LELYSTAD" | org == "WAGENINGEN UNIV \\& RES CTR WUR" | org == "WAGENINGEN UNIV RES CTR" | org == "WAGENINGEN UR" | org == "WAGENINGEN UR LIVESTOCK RES" | org == "WAGENINGEN UR WAGENINGEN LIVESTOCK RES" | org == "UNIV WAGENINGEN" | org == "UNIV WAGENINGEN \\& RES CTR" | org == "CENT VET INST" | org == "CENT VET INST WAGENINGEN UR" | org == "CENT VET INST WAGENMGEN UR",
                                    "WAGENINGEN UNIV", org))
address$org <- with(address, ifelse(org == "WALDECK",
                                    "UNIV FARM ANIM PRACTICE", org))

address$org <- with(address, ifelse(org == "W VIRGINIA SCH MED",
                                    "W VIRGINIA UNIV", org))
address$org <- with(address, ifelse(org == "W TEXAS A\\&M UNIV",
                                    "TEXAS A\\&M UNIV", org))
address$org <- with(address, ifelse(org == "W POMERANIAN UNIV TECHNOL SZCZECIN",
                                    "W POMERANIAN UNIV TECHNOL", org))
address$org <- with(address, ifelse(org == "VYZKUMNY USTAV MLEKARENSKY SRO" | org == "VYZKUMNY USTAV VET LEKARSTVI" | org == "VYZKUMNY USTAV ZIVOCISNE VYROBY",
                                    "VYZKUMNY USTAV", org))

address$org <- with(address, ifelse(org == "VIRGINIA POLYTECH INST \\& STATE UNIV",
                                    "VIRGINIA STATE UNIV", org))
address$org <- with(address, ifelse(org == "VILNIUS STATE UNIV",
                                    "VILNIUS UNIV", org))
address$org <- with(address, ifelse(org == "VIA F DELPINO 1" | org == "UNIV NAPLES FEDERICO 2" | org == "UNIV NAPLES 2" | org == "VIA FEDERICO DELPINO 1",
                                    "UNIV NAPLES FEDERICO II", org))
address$org <- with(address, ifelse(org == "VIA FLLI ROSSELLI 107" | org == "VIA TOLARA SOPRA 50",
                                    "UNIV BOLOGNA", org))
address$org <- with(address, ifelse(org == "VIA S COSTANZO 4",
                                    "UNIV PERUGIA", org))
address$org <- with(address, ifelse(org == "VIA BRECCE BIANCHE",
                                    "UNIV POLITECN MARCHE", org))
address$org <- with(address, ifelse(org == "VIA SAN CAMILLO DE LELLIS",
                                    "UNIV TUSCIA", org))

address$org <- with(address, ifelse(org == "VETSUISSE FAK BERNE" | org == "VETSUISSE FAC BERNA" | org == "VETSUISSE FAK BERN",
                                    "VETSUISSE FAC BERNE", org))
address$org <- with(address, ifelse(org == "VETSUISSE FAC" | org == "UNIV ZURICH VETSUISSE",
                                    "VETSUISSE FAC ZURICH", org))
address$org <- with(address, ifelse(org == "VETMED VIENNA" | org == "VETMEDUNI VIENNA" | org == "VET UNIV VIENNA" | org == "VET MED UNIV VIENNA" | org == "VET MED UNIV WIEN" | org == "UNIV VET MED VETMEDUNI VIENNA" | org == "UNIV VET MED VIENNA" | org == "UNIV MED MED VIENNA" | org == "VET MED UNIV" | org == "VET PL 1" | org == "UNIV CLIN RUMINANTS",
                                    "UNIV VIENNA", org))
address$org <- with(address, ifelse(org == "VETAGRO SUP",
                                    "VETAGRO SUP CLERMONT", org))
address$org <- with(address, ifelse(org == "VET TEACHING HOSP" | org == "UTAD UNIV" | org == "CECAV UTAD" | org == "UNIV TRAS MONTES \\& ALTO DOURO" | org == "UNIV TRAS OS MONTES \\& ALTO DOURO",
                                    "UTAD", org))
address$org <- with(address, ifelse(org == "VET UNIV PERIPHERAL HOSP" | org == "VET UNIV TRAINING \\& RES CTR" | org == "VET COLL RES INST",
                                    "TANUVAS", org))

address$org <- with(address, ifelse(org == "VET LABS AGCY" | org == "VET LABS AGCY SHREWSBURY" | org == "VET LABS AGCY STAPLAKE MT" | org == "VET LABS AGCY THIRSK" | org == "VET LABS AGCY VLA SHREWSBURY" | org == "VET LABS AGCY WEYBRIDGE" | org == "VET LABS AGCY WINCHESTER" | org == "VLA LANGFORD" | org == "VLA PRESTON" | org == "VLA SHREWSBURY" | org == "VLA THIRSK",
                                    "VLA", org))

address$org <- with(address, ifelse(org == "VET MED TEACHING \\& RES CTR",
                                    "UNIV CALIF DAVIS", org))
address$org <- with(address, ifelse(org == "VET SCH" | org == "VET SCH \\& INRA" | org == "VET SCH NANTES" | org == "UMT CATTLE HERD HLTH CONTROL" | org == "UMT SANTE BOVINZ" | org == "UMR" | org == "UMR ONIRIS INRA 1300 BIOEPAR" | org == "UMR ONIRIS INRA1300 BIOEPAR" | org == "ENVN" | org == "ENV NANTES" | org == "ECOLE NATL VET AGROALIMENTAIRE \\& ALIMENTAT ONIRIS",
                                    "ENV NANTES", org))
address$org <- with(address, ifelse(org == "VET SCH TOULOUSE" | org == "UNIV TOULOUSE INPT ENVT" | org == "ENVT" | org == "ENV TOULOUSE" | org == "ECOLE NATL VET TOULOUSE",
                                    "ENV TOULOUSE", org))
address$org <- with(address, ifelse(org == "UNIV TOULOUSE 3",
                                    "UNIV TOULOUSE", org))
address$org <- with(address, ifelse(org == "UNIV THESSALIE",
                                    "UNIV THESSALY", org))
address$org <- with(address, ifelse(org == "UNIV TEHRAN MED SCI",
                                    "UNIV TEHRAN", org))
address$org <- with(address, ifelse(org == "UNIV TECNOL FED PARANA UTFPR",
                                    "UNIV TECNOL FED PARANA", org))
address$org <- with(address, ifelse(org == "UNIV STUDIES BARI ITALY",
                                    "UNIV STUDY BARI", org))
address$org <- with(address, ifelse(org == "UNIV ST CYRIL \\& METHUDIUS" | org == "UNIV SS CYRIL \\& METHODIUS" | org == "UNIV SS CYRILL \\& METHODIUS",
                                    "UNIV ST CYRIL \\& METHODIUS", org))


address$org <- with(address, ifelse(org == "VET INVEST CTR VIC" | org == "VET INVESTIGAT CTR",
                                    "VET INVEST CTR", org))

address$org <- with(address, ifelse(org == "VACCINE \\& INFECT DIS ORG",
                                    "VIDO", org))
address$org <- with(address, ifelse(org == "VET \\& AGROCHEM RES CTR CODA CERVA" | org == "VET \\& AGROCHEM RES CTR VAR CODA CERVA" | org == "VET \\& AGROCHEM RES CTR",
                                    "VAR", org))
address$org <- with(address, ifelse(org == "VEREINIGTE INFORMAT SYST TIERHALTUNG WV" | org == "VEREINIGTE INFORMAT SYST TIERHALTUNG WV VIT",
                                    "VEREINIGTE INFORMAT SYST TIERHALTUNG", org))
address$org <- with(address, ifelse(org == "VET \\& PHARMACEUT SCI BRNO",
                                    "VET \\& PHARMACEUT UNIV BRNO", org))

address$org <- with(address, ifelse(org == "USDA APHIS VS" | org == "NAA ARS USDA" | org == "USDA ARS" | org == "USDA" | org == "USDA AGR RES SERV" | org == "US ANIM \\& PLANT HLTH INSPECT SERV" | org == "USDA APHIS CTR EPIDEMIOL \\& ANIM HLTH",
                                    "USDA", org))
address$org <- with(address, ifelse(org == "USA",
                                    "USAMRIID", org))

address$org <- with(address, ifelse(org == "UNIV UPPSALA HOSP",
                                    "UPPSALA UNIV", org))

address$org <- with(address, ifelse(org == "UNIV WISCONSIN MADISON" | org == "UNIV WISCONSIN MADISON" | org == "MADISON" | org == "UNIV WISCONSIN",
                                    "UW MADISON", org))
address$org <- with(address, ifelse(org == "UNIV YAMANASHI",
                                    "YAMANASHI UNIV", org))

address$org <- with(address, ifelse(org == "UNIV WARMIA \\& MAZURY",
                                    "UNIV WARMIA \\& MAZURIA", org))
address$org <- with(address, ifelse(org == "UNIV WESTERN AUSTRALIA M085",
                                    "UNIV WESTERN AUSTRALIA", org))

address$org <- with(address, ifelse(org == "UNIV SANTIAGO COMPOSTELA",
                                    "UNIV SANTIAGO DE COMPOSTELA", org))

address$org <- with(address, ifelse(org == "UNIV PEDAG \\& TECNOL COLOMBIA",
                                    "UNIV PEDAGOG \\& TECNOL COLOMBIA", org))

address$org <- with(address, ifelse(org == "UNIV LONDON IMPERIAL COLL SCI TECHNOL \\& MED" | org == "UNIV LONDON LONDON SCH HYG \\& TROP MED" | org == "UNIV LONDON ROYAL VET COLL" | org == "ROYAL VET COLL",
                                    "UNIV LONDON", org))

address$org <- with(address, ifelse(org == "UNIV LISBOA ULISBOA",
                                    "UNIV LISBON", org))

address$org <- with(address, ifelse(org == "UNIV LIEGE B34" | org == "UNIV LIEGE GEMBLOUX AGROBIO TECH" | org == "ULG FMV" | org == "GEMBLOUX AGR UNIV" | org == "GEMBLOUX AGR UNIV FUSAGX",
                                    "UNIV LIEGE", org))

address$org <- with(address, ifelse(org == "UNIV HOHENHEIM 480A",
                                    "UNIV HOHENHEIM", org))

address$org <- with(address, ifelse(org == "UNIV GHENT VIB" | org == "UNIV COLL GHENT" | org == "SALISBURYLAAN 133",
                                    "UNIV GHENT", org))

address$org <- with(address, ifelse(org == "UNIV COLL DUBLIN LYONS RES FARM" | org == "UCD VET SCI CTR" | org == "UCD AGR \\& FOOD SCI CTR" | org == "NATL UNIV IRELAND UNIV COLL DUBLIN",
                                    "UNIV COLL DUBLIN", org))

address$org <- with(address, ifelse(org == "UMR 1114 EMMAH INRA" | org == "UMR 1253 SCI \\& TECHNOL LAIT \\& EUF" | org == "UMR 791 INRA AGROPARISTECH MOSAR" | org == "UMR INR AGROPARIS TECH" | org == "UMR INRA" | org == "UMR INRA AGROCAMPUS OUEST 1069 SAS" | org == "UMR INRA ENVA 1198" | org == "UMR PHYSIOL NUTR \\& ALIMENTAT" | org == "INRA AGRO PARIS TECH" | org == "INRA AGROCAMPUS OUEST" | org == "INRA AGROCAMPUS RENNES" | org == "INRA AGROPARIS TECH PHYSIOL NUTR" | org == "INRA AGROPARISTECH" | org == "INRA AGROPARISTECH ENVIRONM \\& GRANDES CULTURES" | org == "INRA AGROPARISTECH UMR PNA" | org == "INRA ASTER MIRECOURT AGROSYST TERR \\& RESSOURCES" | org == "INRA CLERMONT FERRAND THEIX" | org == "INRA DOMAINE VILVERT" | org == "INRA GENPHYSE" | org == "INRA INAPG" | org == "INRA ONIRIS" | org == "INRA SAD" | org == "INRA SADAPT AGROPARISTECH" | org == "INRA SAGA AUZEVILLE" | org == "INRA UMR 1213 HERBIVORES" | org == "INRA UMR 1348 PHYSIOL ENVIRONM \\& GENET ANIM \\& SYS" | org == "INRA UMR DAIRY PROD 1080" | org == "INRA UMR PROD LAIT" | org == "INRA UMR1348 PEGASE" | org == "INRA UMR868" | org == "INRA UNIV BLAISE PASCAL" | org == "INRA UR 1213 HERBIVORES" | org == "INRA UR 631" | org == "INRA UR545 FROMAGERES" | org == "INRA VETAGRO SUP" | org == "INRA VETAGROSUP",
                                    "INRA", org))

address$org <- with(address, ifelse(org == "UMR RUMINANT HUSBANDRY WARM REG",
                                    "CIRAD", org))
address$org <- with(address, ifelse(org == "TINE NORWEGIAN DAIRIES BA" | org == "TINE SA",
                                    "TINE NORWEGIAN DAIRIES", org))
address$org <- with(address, ifelse(org == "TEXAS A\\&M AGRILIFE RES" | org == "TEXAS A\\&M SYST" | org == "TEXAS A\\&M UNIV SOCIOL" | org == "TEXAS A\\&M UNIV SYST",
                                    "TEXAS A\\&M UNIV", org))
address$org <- with(address, ifelse(org == "TECH UNIV MUENCHEN",
                                    "TECH UNIV MUNICH", org))
address$org <- with(address, ifelse(org == "TEAGASC ANIM \\& GRASSLAND \\& INNOVAT RES CTR" | org == "TEAGASC ANIM \\& GRASSLAND RES \\& INNOVAT CTR" | org == "TEAGASC ANIM PROD RES CTR" | org == "TEAGASC ASHTOWN FOOD RES CTR" | org == "TEAGASC DAIRY PROD RES CTR" | org == "TEAGASC ENVIRONM RES CTR" | org == "TEAGASC FOOD RES CTR" | org == "TEAGASC FOOD RES FOOD CTR" | org == "TEAGASC GRANGE BEEF RES CTR" | org == "TEAGASC MOOREPARK DAIRY PROD RES CTR" | org == "TEAGASC MOOREPARK FERMOY CO" | org == "TEAGASC MOOREPK" | org == "TEAGASC MOOREPK FERMOY" | org == "TEAGASC RES CTR",
                                    "TEAGASC", org))
address$org <- with(address, ifelse(org == "SRUC EDINBURGH CAMPUS" | org == "SRUC RES" | org == "SRUC SCOTLANDS RURAL COLL" | org == "SCOTLANDS RURAL COLL" | org == "SCOTLANDS RURAL COLL SRUC" | org == "SCOTLANDS RURAL COLL SRUC RES" | org == "SCOTTISH AGR COLL" | org == "SCOTTISH AGR COLL VET SERV",
                                    "SRUC", org))
address$org <- with(address, ifelse(org == "NOVARTIS ANIM HLTH AUSTRALASIA PTY LTD" | org == "NOVARTIS HEALTHCARE PRIVATE LTD" | org == "NOVARTIS PHARMACEUT",
                                    "NOVARTIS", org))
address$org <- with(address, ifelse(org == "NORWEGIAN SCH ECON \\& BUSINESS ADM" | org == "NORWEGIAN SCH VET MED" | org == "NORWEGIAN SCH VET SCI" | org == "NORWEGIAN UNIV IIFE SCI" | org == "NORWEGIAN UNIV LIFE SCI" | org == "NORWEGIAN COLL VET MED",
                                    "NORWEGIAN UNIV", org))
address$org <- with(address, ifelse(org == "NORWEGIAN INST AGR \\& ENVIRONM RES" | org == "NORWEGIAN INST AGR \\& ENVIRONM RES BIOFORSK",
                                    "BIOFORSK NORWEGIAN INST AGR \\& ENVIRONM RES", org))
address$org <- with(address, ifelse(org == "NESTEC LTD" | org == "NESTLE PURINA RES" | org == "NESTLE R\\&D CTR MINNEAPOLIS" | org == "NESTLE RES CTR",
                                    "NESTLE", org))
address$org <- with(address, ifelse(org == "N CAROLINA AGR \\& TECH STATE UNIV",
                                    "N CAROLINA STATE UNIV", org))
address$org <- with(address, ifelse(org == "MTT AGRIFOOD RES" | org == "MTT AGRIFOOD RES BIOTECHNOL \\& FOOD RES" | org == "MTT AGRIFOOD RES FINALND" | org == "MTT AGRIFOOD RES FINLAND" | org == "MTT AGRIFOOD RES FINLANDD" | org == "MTT AGRIFOOD RES LAND",
                                    "MTT", org))
address$org <- with(address, ifelse(org == "MOOREPARK DAIRY PROD RES CTR" | org == "MOOREPARK RES CTR" | org == "MOOREPK DAIRY PROD RES CTR" | org == "MOOREPK FOOD RES CTR" | org == "MOOREPK PROD RES CTR" | org == "MOOREPK PROD RES CTRA" | org == "MOOREPK RES CTR",
                                    "MOOREPARK CO", org))
address$org <- with(address, ifelse(org == "MONSANTO CO LC",
                                    "MONSANTO CO", org))
address$org <- with(address, ifelse(org == "MERIAL 29 AVE TONY GARNIER" | org == "MERIAL GMBH" | org == "MERIAL LTD" | org == "MERIAL SAS",
                                    "MERIAL", org))
address$org <- with(address, ifelse(org == "IST ZOO PROFILATT SPERIMENTALE LAZIO \\& TOSCANA" | org == "IST ZOOPROFILAT SPERIMENTALE UMBRIA \\& MARCHE" | org == "IST ZOOPROFILATT PIEMONTE LIGURIA \\& VALLE AOSTA" | org == "IST ZOOPROFILATT SPERIMENTALE ABRUZZO \\& MOLISE G" | org == "IST ZOOPROFILATT SPERIMENTALE LAZIO \\& TOSCANA M A" | org == "IST ZOOPROFILATT SPERIMENTALE LOMBARDIA \\& DELLEMI" | org == "IST ZOOPROFILATT SPERIMENTALE LOMBARDIA \\& EMILIA" | org == "IST ZOOPROFILATT SPERIMENTALE MEZZOGIORNO" | org == "IST ZOOPROFILATT SPERIMENTALE PIEMONTE" | org == "IST ZOOPROFILATT SPERIMENTALE PIEMONTE LIGURIA \\&" | org == "IST ZOOPROFILATT SPERIMENTALE PUGLIA \\& BASILICATA" | org == "IST ZOOPROFILATT SPERIMENTALE REG LAZIO \\& TOSCANA" | org == "IST ZOOPROFILATT SPERIMENTALE UMBRIA \\& MARCHE" | org == "IST ZOOPROFILATT SPERIMENTALE VENEZIE" | org == "IST ZOOPROFILATT SPERIMENTALE VENEZIE IZSVE" | org == "IST ZOOPROFILATT VENEZIE" | org == "IST ZOOPROFILATTICO SPERIMENTALE LOMBARDIA \\& EMIL" | org == "IST ZOOPROFILATTICO SPERIMENTALE MEZZOGIORNO" | org == "IST ZOOPROFILATTICO SPERIMENTALE PUGLIA \\& BASILIC" | org == "IST ZOOPROFILATTICO SPERIMENTALE VENEZIE",
                                    "IST ZOOPROFILATT SPERIMENTALE", org))
address$org <- with(address, ifelse(org == "GD" | org == "GD ANIM HLTH SERV" | org == "GD ANIM HLTH SERV DEVENTER" | org == "GD ANIM HLTH SERV LTD" | org == "GD BV" | org == "GD DEVENTER" | org == "GD LTD" | org == "DUTCH ANIM HLTH SERV" | org == "DUTCH UDDER HLTH CTR",
                                    "GD ANIM HLTH", org))
address$org <- with(address, ifelse(org == "FONTERRA COOPERAT GRP LTD" | org == "FONTERRA RES CTR",
                                    "FONTERRA", org))
address$org <- with(address, ifelse(org == "FOOD \\& AGR MAT INSPECT CTR" | org == "FOOD \\& AGR ORG UNITED NAT" | org == "FOOD \\& AGR ORG UNITED NATIONS" | org == "FOOD \\& AGR ORG UNITED NATIONS FAO" | org == "FAO AGAG" | org == "FAO HEADQUARTERS" | org == "FAO IAEA",
                                    "FAO", org))
address$org <- with(address, ifelse(org == "ENVL" | org == "ECOLE NATL VET LYON",
                                    "ENV LYON", org))
address$org <- with(address, ifelse(org == "ECOLE NATL VET" & (reprint_author == "BAREILLE, N" | reprint_author == "BEAUDEAU, F" | reprint_author == "LE BIZEC, B"),
                                    "ENV NANTES", org))
address$org <- with(address, ifelse(org == "ECOLE NATL VET" | org == "ECOLE NATL VET ALFORT",
                                    "ENV MAISONS ALFORT", org))
address$org <- with(address, ifelse(org == "DUPONT NUTR \\& HLTH" | org == "DUPONT PIONEER",
                                    "DUPONT PIONEER", org))
address$org <- with(address, ifelse(org == "DAIRYNZ" | org == "DAIRYNZ LTD" | org == "DAITYNZ LTD" | org == "DAIRY NZ LTD",
                                    "DAIRYNZ", org))
address$org <- with(address, ifelse(org == "CTR DIS CONTROL",
                                    "CTR DIS CONTROL \\& PREVENT", org))
address$org <- with(address, ifelse(org == "CSIRO ADELAIDE LABS" | org == "CSIRO AGR" | org == "CSIRO AGR AUSTRALIAN TROP SCI \\& INNOVAT PRECINCT" | org == "CSIRO AGR COMPUTAT \\& SYST BIOL" | org == "CSIRO ANIM FOOD \\& HLTH SCI" | org == "CSIRO DIGITAL PROD FLAGSHIP" | org == "CSIRO FOOD \\& NUTR FLAGSHIP" | org == "CSIRO FOOD \\& NUTR SCI" | org == "CSIRO FOOD FUTURES FLAGSHIP \\& LIVESTOCK IND" | org == "CSIRO LAND \\& WATER" | org == "CSIRO LIVESTOCK IND" | org == "CSIRO PLANT IND" | org == "CSIRO SUSTAINABLE AGR FLAGSHIP" | org == "CSIRO SUSTAINABLE ECOSYST",
                                    "CSIRO", org))
address$org <- with(address, ifelse(org == "CSIC UCLM JCCM" | org == "CSIC ULE",
                                    "CSIC", org))
address$org <- with(address, ifelse(org == "ALBERTA AGR \\& FOOD" | org == "ALBERTA AGR \\& RURAL DEV" | org == "ALBERTA AGR FOOD \\& RURAL DEV",
                                    "ALBERTA AGR \\& RURAL DEV", org))

address$org <- with(address, ifelse(org == "WILLOW WALK" | org == "VIA ACESSO PAULO DONATO CASTELLANE S-N" | org == "VIA APPIA", "", org))

org <- address$org
org <- sort(org)
table(org[1:100])
address$org <- with(address, ifelse(org == "3200 RUE SICOTTE" |
                                  org == "FAC MED VET", "UNIV MONTREAL", org))
address$org <- with(address, ifelse(org == "1053 CARLING AVE", "OTTAWA HOSP", org))
address$org <- with(address, ifelse(org == "1767 ANGUS CAMPBELL RD", "BC MINIST AGR", org))
address$org <- with(address, ifelse(org == "3400 CASAVANT O", "CFIA", org))
address$org <- with(address, ifelse(org == "50 STONE RD EAST", "OVC", org))
address$org <- with(address, ifelse(org == "550 UNIV AVE", "UPEI", org))
address$org <- with(address, ifelse(org == "6 MAKINS RD", "CTR ECOLOGY AND HYDROLOGY", org))
address$org <- with(address, ifelse(org == "731 PARKDALE AVE", "OHRI", org))
address$org <- with(address, ifelse(org == "AFRC", "INST ANIM HLTH", org))
address$org <- with(address, ifelse(org == "AGR \\& AGRI FOOD CANADA LACOMBE RES CTR" |
                                    org == "AGR \\& AGRIFOOD CANADA" |
                                    org == "AGR \\& AGRIFOOD CANADA RES CTR" |
                                    org == "AGR \\& AGROALIMENTAIRE CANADA" |
                                    org == "AGR \\& FOOD SECUR" |
                                    org == "AGR CANADA" |
                                    org == "BOX 1000" |
                                    org == "DAIRY \\& SWINE R\\&D CTR" |
                                    org == "DAIRY \\& SWINE RES \\& DEV CTR" |
                                    org == "LETHBRIDGE RES CTR" |
                                    org == "MCALLISTER" |
                                    org == "SHERBROOKE RES \\& DEV CTR" |
                                   org == "AGR \\& AGRI FOOD CANADA RES CTR",
                                    "AGR & AGRI FOOD CANADA", org))
address$org <- with(address, ifelse(org == "AGRIFOOD \\& BIOSCI INST",
                                    "AGRI FOOD \\& BIOSCI", org))
address$org <- with(address, ifelse(org == "ALBERTA AGR \\& RURAL DEV AGR CTR" |
                                    org == "ALBERTA AGR \\& RURAL DEV",
                                    "ALBERTA AGR \\& FORESTRY",
                                    org))
address$org <- with(address, ifelse(org == "ALBERTA HLTH SERV PUBL HLTH SURVEILLANCE",
                                    "ALBERTA HLTH SERV", org))
address$org <- with(address, ifelse(org == "AVE DUQUE CAXIAS NORTE 225",
                                    "UNIV SAO PAULO", org))
address$org <- with(address, ifelse(org == "CANADIAN BOVINE MASTITIS RES NETWORK",
                                    "CANADIAN BOVINE MASTITIS \\& MILK QUAL RES NETWORK",
                                    org))
address$org <- with(address, ifelse(org == "CANADIAN FOOD INSPECT AGCY",
                                    "CFIA",
                                    org))
address$org <- with(address, ifelse(org == "ANIM \\& PLANT HLTH AGCY" |
                                    org == "ANIM \\& PLANT HLTH INSPECT SERV",
                                    "USDA",
                                    org))
address$org <- with(address, ifelse(org == "ANIM HLTH \\& VET LABS AGCY" |
                                    org == "ANIM HLTH \\& VET LABS AGCY AHVLA" |
                                    org == "ANIM PLANT HLTH INSPECT SERV" |
                                    org == "APHA WEYBRIDGE",
                                    "AHVLA",
                                    org))
address$org <- with(address, ifelse(org == "CANADIAN FOOD INSPECT AGCY",
                                    "CFIA",
                                    org))
address$org <- with(address, ifelse(org == "CANADIAN FOREST SERV",
                                    "NAT RESOURCES CANADA",
                                    org))
address$org <- with(address, ifelse(org == "CLIN PEDIAT B TRAMBUSTI PIAZZA GIULIO CESARE",
                                    "CLIN PEDIAT B TRAMBUSTI",
                                    org))
address$org <- with(address, ifelse(org == "CSIRO CAFHS",
                                    "CSIRO",
                                    org))
address$org <- with(address, ifelse(org == "CTR IRD",
                                    "MIGEVEC",
                                    org))
address$org <- with(address, ifelse(org == "DEPT VET MICROBIOL",
                                    "WCVM",
                                    org))
address$org <- with(address, ifelse(org == "DEPT ZOOTECNIA",
                                    "UNESP",
                                    org))
address$org <- with(address, ifelse(org == "ENVIRONM \\& CLIMATE CHANGE CANADA",
                                    "ENVIRONM CANADA",
                                    org))
address$org <- with(address, ifelse(org == "FAC EXTENS" |
                                   org == "FAC VET MED",
                                    "UNIV CALGARY",
                                    org))
address$org <- with(address, ifelse(org == "FAC VET \\& AGR SCI",
                                    "UNIV MELBOURNE",
                                    org))
address$org <- with(address, ifelse(org == "FCAV UNIV ESTADUAL PAULISTA",
                                    "UNESP",
                                    org))
address$org <- with(address, ifelse(org == "FRIEDRICH LOEFFLER INST FLI",
                                    "FRIEDRICH LOEFFLER INST",
                                    org))
address$org <- with(address, ifelse(org == "GE",
                                    "CHINA PHARMACEUT UNIV",
                                    org))
address$org <- with(address, ifelse(org == "INST ARMAND FRAPPIER",
                                    "INRS INST ARMAND FRAPPIER",
                                    org))
address$org <- with(address, ifelse(org == "JL SHUTE BLDG",
                                    "UNIV SYDNEY",
                                    org))
address$org <- with(address, ifelse(org == "KARROW",
                                    "UNIV GUELPH",
                                    org))
address$org <- with(address, ifelse(org == "KING SAUD BIN ABDULAZIZ UNIV HLTH SCI",
                                    "KING SAUD UNIV",
                                    org))
address$org <- with(address, ifelse(org == "LOOR",
                                    "UNIV ILLINOIS",
                                    org))
address$org <- with(address, ifelse(org == "MAISONNEUVE ROSEMONT HOSP" |
                                   org == "MAISONNEUVE ROSEMONT HOSP RES CTR" |
                                   org == "HOP MAISON NEUVE ROSEMONT",
                                   "UNIV MONTREAL",
                                    org))
address$org <- with(address, ifelse(org == "MCGILL UNIV HLTH CTR" |
                                   org == "ROYAL VICTORIA HOSP H6 19",
                                    "MCGILL UNIV",
                                    org))
address$org <- with(address, ifelse(org == "NATL ANIM DIS CTR" |
                                    org == "NATL CTR FOREIGN ANIM DIS" |
                                   org == "CANADIAN FOOD INSPECT AGENCY",
                                    "CFIA",
                                    org))
address$org <- with(address, ifelse(org == "NATL MICROBIOL LAB" |
                                   org == "PHAC LFZ",
                                    "PHAC",
                                    org))
address$org <- with(address, ifelse(org == "PK CANADA AGCY",
                                    "UNIV SASKATCHEWAN",
                                    org))
address$org <- with(address, ifelse(org == "POB 16146",
                                    "SEQWATER",
                                    org))
address$org <- with(address, ifelse(org == "POB 22490",
                                    "KING SAUD UNIV",
                                    org))
address$org <- with(address, ifelse(org == "POB 29053-00625",
                                    "UNIV NAIROBI",
                                    org))
address$org <- with(address, ifelse(org == "PROV LAB PUBL HLTH",
                                    "ALBERTA HLTH SERV",
                                    org))
address$org <- with(address, ifelse(org == "PHAC",
                                    "PUBL HLTH AGCY CANADA",
                                    org))
address$org <- with(address, ifelse(org == "PUBL HLTH ONTARIO LABS",
                                    "PUBL HLTH ONTARIO",
                                    org))
address$org <- with(address, ifelse(org == "ROYAL UNIV HOSP" |
                                    org == "UNIV SASKACHEWAN" |
                                   org == "WCVM",
                                    "UNIV SASKATCHEWAN",
                                    org))
address$org <- with(address, ifelse(org == "SAO PAULO STATE UNIV FCAV UNESP" |
                                    org == "UNESP UNIV ESTADUAL PAULISTA" |
                                    org == "UNIV ESTADUAL PAULISTA" |
                                   org == "UNIV ESTADUAL PAULISTA UNESP",
                                    "UNESP",
                                    org))
address$org <- with(address, ifelse(org == "ST BONIFACE GEN HOSP",
                                    "UNIV MANITOBA",
                                    org))
address$org <- with(address, ifelse(org == "UNIV NACL CTR PROV BUENOS AIRES" |
                                    org == "UNIV NACL CTR PROV BUENOS AIRES UNICEN",
                                    "UNICEN",
                                    org))
address$org <- with(address, ifelse(org == "UNIV VET MED",
                                    "UNIV VET MED HANNOVER",
                                    org))
address$org <- with(address, ifelse(org == "UPEI",
                                    "UNIV PRINCE EDWARD ISL",
                                    org))
address$org <- with(address, ifelse(org == "USDA ARS PLUM ISL ANIM DIS CTR" |
                                   org == "PLUM ISL ANIM DIS CTR",
                                    "USDA",
                                    org))
address$org <- with(address, ifelse(org == "VACCINE INFECT DIS ORG INT VACCINE CTR VIDO INTER" | org == "VIDO",
                                    "VACCINE INFECT DIS ORG",
                                    org))
address$org <- with(address, ifelse(org == "VON KEYSERLINGK",
                                    "UNIV BRITISH COLUMBIA",
                                    org))
address$org <- with(address, ifelse(org == "WILLE" | org == "307",
                                    "UNIV ALBERTA",
                                    org))
address$org <- with(address, ifelse(org == "OVC",
                                    "UNIV GUELPH",
                                    org))
address$org <- with(address, ifelse(org == "AGR \\& AGRI FOOD CANADA",
                                    "AGR & AGRI FOOD CANADA",
                                    org))
address$org <- with(address, ifelse(org == "ALBERTA AGR \\& FORESTRY",
                                    "ALBERTA AGR & FORESTRY",
                                    org))
address$org <- with(address, ifelse(org == "KM 40 CARRETERA COLIMA MANZANILLO",
                                    "UCOL",
                                    org))
```

```{r, eval=FALSE}
D <- readFiles("records.bib")
M <- convert2df(D, dbsource = "isi", format = "bibtex")

results <- biblioAnalysis(M, sep = ";")
```

So we've got 1569 articles and 114 reviews, from 5157 authors.

```{r}
results$Articles  ## number of articles
results$nAuthors  ## number of authors
```

There's a generic `summary` function that provides overall results of the
bibliographic analysis:

```{r}
S <- summary(results, k = 10, pause = FALSE)
```

Thanks to `stringr` package, I could fix the address information of the authors
to get the following graphs.

```{r, echo=FALSE, fig.cap="Evolution of publications in cattle health research."}
freq_pub <- as.data.frame(table(results$Years))
freq_pub$Var1 <- as.integer(as.character(freq_pub$Var1))

ggplot(freq_pub, aes(x = Var1, y = Freq)) + 
    geom_line(colour=ggthemes_data$fivethirtyeight["red"]) +
    scale_x_continuous(breaks = 2012:2017) + 
    geom_point(colour=ggthemes_data$fivethirtyeight["red"]) + 
    theme_fivethirtyeight() + 
    theme(axis.title=element_text(face="bold"),
          plot.title=element_text(size=14)) +
    xlab("Years") + 
    ylab("Publications") +
    ggtitle("Evolution of publications in cow health research",
            subtitle="From January 2012 to October 2017") +
    theme(axis.text.y = element_text(colour = "grey42")) + 
    theme(axis.text.x = element_text(colour="grey42"))
```

```{r, echo=FALSE, fig.cap="The 10 most productive research groups."}
freq_org <- as.data.frame(sort(table(address$org), decreasing = TRUE))

ggplot(freq_org[1:10, ], aes(x = Var1, y = Freq)) + 
    geom_bar(stat = "identity", fill=ggthemes_data$fivethirtyeight["red"]) +
    theme_fivethirtyeight() + 
    theme(axis.title=element_text(face="bold"),
          plot.title=element_text(size=14)) +
    ylab("Publications") +
    ggtitle("Most productive research groups",
            subtitle="From January 2012 to October 2017") +
    theme(axis.text.y = element_text(colour = "grey42")) + 
    theme(axis.text.x = element_text(angle = 65, hjust = .5, vjust = .5,
                                     colour="grey42")) +
    theme(axis.title.x = element_blank())
```

Note that 2017 is not over yet, so explaining the drop in the number of
publications in the first figure.

The most productive group is the University of Guelph, closely followed by
Agriculture and Agri-Food Canada.

## Measure of collaboration

Dominance factor (DF) can be computed, according to the formula of [Kumar & Kumar,
2008](http://www.collnet.de/Berlin-2008/KumarWIS2008cir.pdf).
This factor gives an indication of the collaboration in the field, as a ratio of
the number of multi-authored articles in which a scholar appears as first author
to the total number of multi-authored articles.
A value of less than 0.5 reflects a good sign for collaboration; high value
shows more dominance of author as first author.

```{r}
DF <- dominance(results, k = 10)
DF
```

All authors in the field look like they're quite collaborative.
Buczinski (Universit de Montral) and Stanford (Alberta Agriculture & Forestry)
dominate their research team because they appear as first authors in a large
proportion of their papers (10 out of 26 for Buczinski and 9 out of 28 for Stanford).

## Authors' h-index

The h-index tries to measure both the number of publications a researcher
produced ("quantity") and their impact on other publications ("quality").
Here's my own and the ones from the 30 most productive authors, in this
collection.

```{r}
indices <- Hindex(M, authors = "HAINE D", sep = ";", years = 10)
## Haine's impact indices:
indices$H
# Haine's citations
indices$CitationList

## h-index of the first 30 most productive authors in this collection
authors=gsub(",", " ", names(results$Authors)[1:30])
indices <- Hindex(M, authors, sep = ";", years = 50)
indices$H
```

My h-index is 3 (all time 11 on [Google
Scholar](https://scholar.google.com/citations?user=KFeLZyIAAAAJ&hl=en), and
I have 3 other papers in press, not yet included in this collection, and you
need some time for papers to get cited).
Barkema, Orsel (University of Calgary), LeBlanc, Leslie, Kelton, Chapinal
(University of Guelph), McAllister, Rushen, Beauchemin (Agriculture and
Agri-Food Canada), Weary (University of British Columbia), and Miglior (Canadian
Dairy Network) have the largest h-index among the top 30 most productive
authors.
However we see h-index of zero for Von Keyserlingk (University of British
Columbia), De Buck (University of Calgary), and De Passill (Agriculture and
Agri-Food Canada).
My guess is that their name is wrongly filtered, resulting in a wrong
computation of their h-index (Von Keyserlingk and De Buck have 42 and 21 on
Google Scholar, respectively. Couldn't find De Passill).

## Bilbiometric network matrices

This is where it's getting interesting: analysing the networks based on the
attributes of the bibliometric data.

### Authors' collaboration

```{r, echo=FALSE, fig.width=12, fig.height=12, fig.cap="Authors' collaboration."}
NetMatrix_COL <- biblioNetwork(M, analysis = "collaboration",
                               network = "authors", sep = ";")
net_AU <- networkPlot(NetMatrix_COL, n = 50, Title = "Authors' Collaboration",
                      type = "kamada", size = TRUE, halo = TRUE)
```

Different communities appear, around 2 PIs: Barkema and McAllister (remember
from above, these two are very productive and have a low DF).
Barkema is centered across 2 communities (in green and yellow).
Interestingly, the blue community is mainly from eastern Canada (Universit de
Montral, University of Prince Edward Island), while the green one is more
western (University of Guelph, University of Calgary, University of British
Columbia).
In both case, authors are working on a variety of topics: clinical diseases
(i.e. Fecteau, Francoz), epidemiology (i.e. Dohoo, Pearl), production (LeBlanc),
animal sciences (Pellerin, Vasseur), animal welfare (De Vries, Von Keyserlingk),
etc.
But in most cases, it looks like they're doing field work.
While around McAllister, it looks like it's more lab work.
This would need digging deeper, but it's a rough first approximation.

### Organisations' collaboration

```{r, echo=FALSE, fig.width=12, fig.height=12, fig.cap="Organisations' collaboration."}
M_org <- metaTagExtraction(M, Field = "AU_UN", sep = ";")
NetMatrix_ORG <- biblioNetwork(M_org, analysis = "collaboration",
                               network = "universities", sep = ";")
net_ORG <- networkPlot(NetMatrix_ORG, n = 25, Title = "Organisations' Collaboration",
                       type = "kamada", size = TRUE)
```

Collaboration is mainly realised between Canadian institutions, with only one
from Europe (University of Ghent, Belgium), and 6 from the US (Kansas State
University, Colorado State University, University of Florida, University of
California in Davis, Iowa State University, and University of Minnesota).

### Author keyword co-occurrences

```{r, echo=FALSE, fig.width=12, fig.height=12, fig.cap="Author keyword co-occurrences."}
NetMatrix_kw <- biblioNetwork(M, analysis = "co-occurrences",
                              network = "author_keywords", sep = ";")
kw_net <- networkPlot(NetMatrix_kw, n = 20, Title = "Author Keywords Co-occurrences",
                      type = "kamada", size = TRUE)
```

According to keywords provided by the authors, we find the usual research themes
in cattle health: mastitis, welfare, lameness, Johne's, BRD.

### Co-word analysis: conceptual structure of the field

Here we're mapping the conceptual structure of the field using the word
co-occurrences in the bibliographic collection, by performing a MCA and K-means
clustering to identify clusters of documents which express common concepts.

```{r, echo=FALSE, fig.width=12, fig.height=12, fig.cap="Conceptual structure of the field."}
CS <- conceptualStructure(M_org, field = "DE_TM", minDegree = 12, k.max = 5,
                          stemming = FALSE, labelsize = 10)
```

Four fields emerge, one specific to paratuberculosis, one for contagious
diseases, one for production diseases and performances, and one probably for
genetics.

## Final word

This was a rough tentative of exploring Canadian research on cattle health.

Eh! in Canada, you're either in the gang of Barkema, or McAllister... `r emo::ji("wink")`
